%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.80]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Ossama}{Edbali}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{37 Hullbrook Road}{B13 0LA, Birmingham}{UK}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+44~(0)7481~551062}                   % optional, remove / comment the line if not wanted
\email{ossedb@gmail.com}                               % optional, remove / comment the line if not wanted
\homepage{oss6.github.io}                         % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Education}
\cventry{2014--2018}{MSci Computer Science}{University Of Birmingham}{Birmingham, UK}{}
{
\begin{itemize}
\item First year passed with average of 85\% including 100\% in Robot programming, 99\% in Information and the Web, 92\% in Software Workshop and 83\% in Language and Logic.
\item Programming languages covered: Java, C/C++, OCaml and Haskell.
\item Software engineering topics: agile methodology, TDD, UML, refactoring and design patterns.
\end{itemize}
}  % arguments 3 to 6 can be left empty
\cventry{2008--2014}{High School}{G. Marconi IT Institute}{Rovereto, Italy}{\textit{100/100 overall - 15/15 in Computer Science}}
{
I attended a professional Computer Science Institute in high school. The CS syllabus was as follows:
\begin{itemize}
\item Foundations of Computer Science: algorithms, data structures, OOP, UML and MVC architecture.
\item Database Theory: Entity-Relationship diagrams, transactions, ACID, relational algebra.
\item Networks: TCP/IP model, OSI model, ARP, ICMP, SSL/TLS, DNS, Socket programming etc\dots
\end{itemize}
}

\section{Skills profile}
\cvitem{Programming languages and tools}
{
\begin{itemize}
\item Strong knowledge in: C\#, Java, Python, PHP, SQL, JavaScript and R - 5 years of experience.
\item Experience using version control system: Git (following industry standards on branching model).
\item Unit testing using the appropriate test suites for each language (for example TestNG in Java).
\item Worked on projects involving LAMP and LEMP stacks using Vagrant and Chef for setting up replicable development environments. Worked on MEAN stack web apps and variations of it.
\end{itemize}
}
\cvitem{Web technologies}
{
\begin{itemize}
\item Django MVC (Python) - implemented bioimaging APIs, learning management systems and protein-protein interaction network visualisation.
\item PHP Laravel / Symfony / CodeIgniter / NodeJS - implemented MySQL web-based clients, SOAP web services and courier platforms.
\item On the frontend side I am proficient in AngularJS, BackboneJS and Polymer.
\end{itemize}
}
\cvitem{Databases}{Worked on projects using MySQL, MongoDB and PostgreSQL (GIS datasets). My main focus is on database optimisation and table refactoring.}

\section{Work experience}
\cventry{January 2016--Present}{Instructor}{Code First: Girls}{Birmingham, UK}{}{Frontend website development lead instructor.\newline{}
\begin{itemize}
\item Deliver the course and take the students through the teaching material and competition.
\item Track student progress and assess understanding through
targeted questions.
\item Support the course ambassadors with their socials activities.
\item Provide additional support whenever needed.
\item Nominated as the Instructor of the month of April 2016.
\end{itemize}
}

\newpage

\cventry{June 2015--Present}{Student Ambassador}{University Of Birmingham}{Birmingham, UK}{}{
\begin{itemize}
\item Student Ambassador helping with UG Open Days, Applicant Visit Days, Careers Fairs and other events.
\item This role has further developed my communication as well as my team working skills.
\end{itemize}
}

\cventry{July 2015--September 2015}{Web developer}{Codemakers Ltd}{Derby, UK}{}{Full time backend web developer.
\newline{}
\begin{itemize}
\item Web and API development using Laravel (API development) and CodeIgniter (SOAP web services).
\item Refactoring and porting previous projects.
\item I improved my skills in git workflow, unit testing of web applications using external resources (such as DB), design patterns (repository, facade and dependency injection) and team interaction.
\end{itemize}
}

\cventry{August 2014--October 2014}{Web developer}{Codemakers Ltd}{Derby, UK}{}{Worked as an intern in web development and database optimisation.
\newline{}
\begin{itemize}
\item Database and web application optimisation: query optimisations and network requests inspections.
\item Web design and development: for specific info about the projects I worked on please contact me.
\item I improved my skills in detecting "bad code smells", refactoring and JavaScript performance monitoring.
\end{itemize}
}

\cventry{May 2015}{Training}{Mitsubishi Electric}{Cracow, Poland}{}{Mitsubishi Electric FA Centre training for students.
\newline{}
\begin{itemize}
\item Took part in a two-weeks "full immersion" course at the Mitsubishi Electric of Cracow.
\item The aim of the project was to improve the students’ skills in the field of robotic industry and automation.
\item Topics: Programming industrial robots (4 and 6 axis - SCARA), PLCs, Inverters and design of simple HMIs (Human Machine Interface) using GOT 1000 series.
\end{itemize}
}

\cventry{June 2013--July 2013}{Researcher}{Web Valley, FBK}{Castello di Fiemme, Italy}{}{Worked with a team of young researchers from around the world to implement a web platform for bioimaging.
\newline{}
\begin{itemize}
\item The aim was designing a novel web tool for studying change in cells (e.g. in morphogenesis or in disease) from different points of view and in interdisciplinary teams.
\item My team was in charge of developing the API structure and the web interface (using Django Python). The biological data came from studies of a group of international researchers and scientists (Lani Wu and Stephen Altschuler - Texas University, Anna Alisi - Ospedale Pediatrico Bambino Gesù, Gabriella Rustici - European Biological Institute).
\item I learned how to work with various team with diverse background skills. My team’s task was to to gather requirements from other teams in order to build a functioning API.
\item For more information: \url{https://webvalley.fbk.eu/}
\end{itemize}
}

\cventry{June 2013}{Web developer and analyst intern}{Comunità della Vallagarina}{Rovereto, Italy}{}{Worked as an intern in the IT and environment departments in Rovereto City Council
\newline{}
\begin{itemize}
\item Developed the mobile version of the already existing desktop website using jQuery Mobile.
\item Developed some useful JavaScript widgets in the ecology section (autocomplete, pagination etc\ldots).
\item Gather, analyse ecological data and produce detailed reports on the city council waste disposal.
\end{itemize}
}

\section{Languages skills}
\cvitemwithcomment{Mother tongue(s)}{Italian, Arabic}{}
\cvitemwithcomment{Other language(s)}{English - C1 (IELTS), German (Elementary proficiency)}{}

%\section{Computer skills}
%\cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
%\cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}
%
%\section{Interests}
%\cvitem{hobby 1}{Description}
%\cvitem{hobby 2}{Description}
%\cvitem{hobby 3}{Description}
%
%\section{Extra 1}
%\cvlistitem{Item 1}
%\cvlistitem{Item 2}
%\cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}
%
%\section{Extra 2}
%\cvlistdoubleitem{Item 1}{Item 4}
%\cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
%\cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}
%
%\section{References}
%\begin{cvcolumns}
%  \cvcolumn{Category 1}{\begin{itemize}\item Person 1\item Person 2\item Person 3\end{itemize}}
%  \cvcolumn{Category 2}{Amongst others:\begin{itemize}\item Person 1, and\item Person 2\end{itemize}(more upon request)}
%  \cvcolumn[0.5]{All the rest \& some more}{\textit{That} person, and \textbf{those} also (all available upon request).}
%\end{cvcolumns}

\end{document}


%% end of file `template.tex'.
